---
title: inclass-week7
author: Ziyang Ye
format:
    html:
        code-fold: False
        embed-resources: true
        self-contained: true
        theme:
            light: [cosmo, theme.scss]
            dark: [cosmo, theme-dark.scss]
        toc: true
---

### Activity 1

(base) ziyangs-MacBook-Pro:stat778-week7 ziyangye$ ls
778-week7-inclass.qmd   README.md               lecture_07-hpc.html

### Activity 2

This is what my R script looks like:
```{r}
library(argparser)

# Create a parser with a brief description.
p <- arg_parser("A brief description of what this Rscript does.")

# Add named arguments.
p <- add_argument(p, "--ncores", type = "integer", default = 1L,
                  help = "Number of CPUs to use for parallel processing")
p <- add_argument(p, "--repl", type = "integer", default = 1L,
                  help = "Number of replications to run")

# Add positional (unnamed) argument.
p <- add_argument(p, "task", type = "integer", 
                  help = "Task number")

# Parse the arguments.
args <- parse_args(p)

# Report the number of CPUs.
cat("Running code on", args$ncores, "CPUs\n")

# Create an output file name from repl and task.
output_file <- paste0("results_repl", args$repl, "_task", args$task, ".txt")

# Print the output file name with a short description.
cat("Results will be saved to file:", output_file, "\n")

```
This script now:

Accepts the named argument --ncores (integer),
Accepts the named argument --repl (integer),
Accepts the positional argument task (integer),
Constructs an output file name using the values of repl and task,
And prints both the CPU information and the output file name to the standard output.

output:
(base) ziyangs-MacBook-Pro:stat778-week7 ziyangye$ Rscript myrscript.R --ncores 1 --repl 10 2
Running code on 1 CPUs
Results will be saved to file: results_repl10_task2.txt



### Activity 3


(base) ziyangye@ziyangs-MacBook-Pro ~ % ssh -v hopper
OpenSSH_9.0p1, LibreSSL 3.3.6
debug1: Reading configuration data /Users/ziyangye/.ssh/config
debug1: /Users/ziyangye/.ssh/config line 2: Applying options for hopper
debug1: Reading configuration data /etc/ssh/ssh_config
debug1: /etc/ssh/ssh_config line 21: include /etc/ssh/ssh_config.d/* matched no files
debug1: /etc/ssh/ssh_config line 54: Applying options for *
debug1: /etc/ssh/ssh_config line 58: Applying options for *
debug1: Authenticator provider $SSH_SK_PROVIDER did not resolve; disabling
debug1: Connecting to hopper.orc.gmu.edu port 22.
debug1: Connection established.
debug1: identity file /Users/ziyangye/.ssh/orc-hpc.key type -1
debug1: identity file /Users/ziyangye/.ssh/orc-hpc.key-cert type -1
debug1: Local version string SSH-2.0-OpenSSH_9.0
debug1: Remote protocol version 2.0, remote software version OpenSSH_8.0
debug1: compat_banner: match: OpenSSH_8.0 pat OpenSSH* compat 0x04000000
debug1: Authenticating to hopper.orc.gmu.edu:22 as 'zye2'
debug1: load_hostkeys: fopen /Users/ziyangye/.ssh/known_hosts2: No such file or directory
debug1: load_hostkeys: fopen /etc/ssh/ssh_known_hosts: No such file or directory
debug1: load_hostkeys: fopen /etc/ssh/ssh_known_hosts2: No such file or directory
debug1: SSH2_MSG_KEXINIT sent
debug1: SSH2_MSG_KEXINIT received
debug1: kex: algorithm: curve25519-sha256
debug1: kex: host key algorithm: ssh-ed25519
debug1: kex: server->client cipher: chacha20-poly1305@openssh.com MAC: <implicit> compression: none
debug1: kex: client->server cipher: chacha20-poly1305@openssh.com MAC: <implicit> compression: none
debug1: expecting SSH2_MSG_KEX_ECDH_REPLY
debug1: SSH2_MSG_KEX_ECDH_REPLY received
debug1: Server host key: ssh-ed25519 SHA256:15A/UGidvu+9lbhU08h43jlNm6XGcT/gYSe2ndmGPqs
debug1: load_hostkeys: fopen /Users/ziyangye/.ssh/known_hosts2: No such file or directory
debug1: load_hostkeys: fopen /etc/ssh/ssh_known_hosts: No such file or directory
debug1: load_hostkeys: fopen /etc/ssh/ssh_known_hosts2: No such file or directory
debug1: Host 'hopper.orc.gmu.edu' is known and matches the ED25519 host key.
debug1: Found key in /Users/ziyangye/.ssh/known_hosts:13
debug1: rekey out after 134217728 blocks
debug1: SSH2_MSG_NEWKEYS sent
debug1: expecting SSH2_MSG_NEWKEYS
debug1: SSH2_MSG_NEWKEYS received
debug1: rekey in after 134217728 blocks
debug1: get_agent_identities: bound agent to hostkey
debug1: get_agent_identities: ssh_fetch_identitylist: agent contains no identities
debug1: Will attempt key: /Users/ziyangye/.ssh/orc-hpc.key  explicit
debug1: SSH2_MSG_EXT_INFO received
debug1: kex_input_ext_info: server-sig-algs=<ssh-ed25519,ssh-rsa,rsa-sha2-256,rsa-sha2-512,ssh-dss,ecdsa-sha2-nistp256,ecdsa-sha2-nistp384,ecdsa-sha2-nistp521>
debug1: SSH2_MSG_SERVICE_ACCEPT received
|====================================================================|
| Use of this computer system without authority, or in excess of     |
| granted authority, is prohibited.  This system monitored and       |
| recorded by system personnel.                                      |
|                                                                    |
| Wait for Duo 2FA                                                   |
|====================================================================|
debug1: Authentications that can continue: publickey,gssapi-with-mic,password
debug1: Next authentication method: publickey
debug1: Trying private key: /Users/ziyangye/.ssh/orc-hpc.key
no such identity: /Users/ziyangye/.ssh/orc-hpc.key: No such file or directory
debug1: Next authentication method: password
zye2@hopper.orc.gmu.edu's password: 
Authenticated using "password" with partial success.
debug1: Authentications that can continue: publickey,gssapi-with-mic,keyboard-interactive
debug1: Next authentication method: keyboard-interactive
Authenticated to hopper.orc.gmu.edu ([129.174.21.130]:22) using "keyboard-interactive".
debug1: channel 0: new [client-session]
debug1: Requesting no-more-sessions@openssh.com
debug1: Entering interactive session.
debug1: pledge: filesystem
debug1: client_input_global_request: rtype hostkeys-00@openssh.com want_reply 0
debug1: client_input_hostkeys: searching /Users/ziyangye/.ssh/known_hosts for hopper.orc.gmu.edu / (none)
debug1: client_input_hostkeys: searching /Users/ziyangye/.ssh/known_hosts2 for hopper.orc.gmu.edu / (none)
debug1: client_input_hostkeys: hostkeys file /Users/ziyangye/.ssh/known_hosts2 does not exist
debug1: client_input_hostkeys: no new or deprecated keys from server
debug1: Sending environment.
debug1: channel 0: setting env LANG = "en_US.UTF-8"
Autopushing login request to phone...
Success. Logging you in...
Last failed login: Thu Mar  6 16:53:51 EST 2025 from 72.83.26.85 on ssh:notty
There was 1 failed login attempt since the last successful login.
Last login: Thu Mar  6 16:53:10 2025 from 72.83.26.85
|--------------------------------------------------------------------|
|                     HOPPER RESEARCH CLUSTER                        |
|          _  _ ____ ___  ___  ____ ____    ____ _  _ ___            | 
|          |__| |  | |__] |__] |___ |__/ __ |__| |\/| |  \           |
|          |  | |__| |    |    |___ |  \    |  | |  | |__/           |
|                                                                    |
|   *** George Mason University - Office of Research Computing ***   |
|                                                                    |
| Use of this computer system without authority, or in excess of     |
| granted authority, is prohibited.  This system monitored and       |
| recorded by system personnel.                                      |
|                                                                    |
| Use of this system is subject to the agreement that any research   |
| produced is in the public domain, and is intended to be published  |
| or is at least able to be published without restriction.           |
|--------------------------------------------------------------------|
* $SCRATCH directory has time quota of 90 days.                      *
*    ANY data older than 90 days will be deleted on the 1st day of   *
*    each month. $SCRATCH is not backed up.                          *
*                                                                    *
* Due to high GPU demand,A100.80 and A100.40 GPUs are now available  *
*  only to jobs submitted using Slurm scripts.Interactive GPU        *
*  sessions using salloc or Open OnDemand are limited to 1g.10gb,    *
*  2g.20gb,and 3g.40gb MIG GPU slices.                               *
*                                                                    *
* SLURM maximum time limits have been increased for these partitions:*
*  - normal = 5 days (#SBATCH --time=5-00:00:00)                     *
*  - gpuq   = 3 days (#SBATCH --time=3-00:00:00)                     *
**********************************************************************
[zye2@hop-amd-1 ~]$ 







[zye2@hop-amd-1 ~]$ module spider r

----------------------------------------------------------------------------
  r:
----------------------------------------------------------------------------
     Versions:
        r/3.6.3
        r/4.0.3-hb
        r/4.0.3-hx
        r/4.0.3-pn
        r/4.0.3-ta
        r/4.1.2-dx
        r/4.1.2-zx
        r/4.3.1-gnu-mkl
        r/4.3.1-gnu-openblas
        r/4.3.1-intel-mkl
        r/4.3.1-singularity
        r/4.3.2-gnu-openblas
        r/4.4.0-ba
     Other possible modules matches:
        .charliecloud  .compiler-rt32  .compiler32  admixture  advisor  ...

----------------------------------------------------------------------------
  To find other possible module matches execute:

      $ module -r spider '.*r.*'

----------------------------------------------------------------------------
  For detailed information about a specific "r" package (including how to load the modules) use the module's full name.
  Note that names that have a trailing (E) are extensions provided by other modules.
  For example:

     $ module spider r/4.4.0-ba
----------------------------------------------------------------------------

 


### Activity 4


[zye2@hop-amd-1 zye2]$ git clone https://github.com/ZiyangYe566842/stat778-week7.git
Cloning into 'stat778-week7'...
remote: Enumerating objects: 14, done.
remote: Counting objects: 100% (14/14), done.
remote: Compressing objects: 100% (9/9), done.
remote: Total 14 (delta 3), reused 10 (delta 2), pack-reused 0 (from 0)
Receiving objects: 100% (14/14), 283.03 KiB | 28.30 MiB/s, done.
Resolving deltas: 100% (3/3), done.
[zye2@hop-amd-1 zye2]$ ls
stat778-week7  tmp
[zye2@hop-amd-1 zye2]$ 

[zye2@hop-amd-1 stat778-week7]$ Rscript myrscript.R --ncores 1 --repl 10 2
Loading required package: argparser
Running code on 1 CPUs
Results will be saved to file: results_repl10_task2.txt



### Activity 5
```{r}
#!/usr/bin/env Rscript

user_lib <- "~/Rlibs"
if (!dir.exists(user_lib)) {
  dir.create(user_lib, recursive = TRUE)
}
.libPaths(c(user_lib, .libPaths()))


install_if_missing <- function(pkg) {
  if (!suppressWarnings(require(pkg, character.only = TRUE))) {
    message("Package ", pkg, " not found. Installing...")
    install.packages(pkg, repos = "https://cloud.r-project.org", lib = user_lib)
    library(pkg, character.only = TRUE)
  }
}

install_if_missing("argparser")
install_if_missing("robustbase")


suppressPackageStartupMessages({
  library(argparser)
})
p <- arg_parser("Estimate AR(1) correlation coefficient using MCD")
p <- add_argument(p, "--ncores", help="Number of cores (not used in this script)", type="integer", default=1)
p <- add_argument(p, "--repl", help="Number of replications", type="integer", default=10)
p <- add_argument(p, "--task", help="Task number (1-10) for AR(1) coefficient grid", type="integer", default=1)
argv <- parse_args(p)

grid <- seq(0.09, 0.99, length.out = 10)
rho <- grid[argv$task]
cat("Using AR(1) coefficient (rho) =", rho, "\n")

d <- 200

corr_matrix <- outer(1:d, 1:d, FUN = function(i, j) rho^abs(i - j))

L <- chol(corr_matrix)


n <- 400
results_list <- vector("list", argv$repl)
set.seed(123)

for (rep in 1:argv$repl) {

  X <- matrix(rt(n * d, df = 2), nrow = n, ncol = d)

  Y <- X %*% t(L)
  

  mcd <- covMcd(Y)
  corr_est <- cov2cor(mcd$cov)

  first_superdiag <- sapply(1:(d - 1), function(i) corr_est[i, i + 1])
  results_list[[rep]] <- first_superdiag
}


saveRDS(results_list, file = "myrscript.rds")
cat("Results saved to myrscript.rds\n")

```

### Activity 6
#!/bin/bash
#SBATCH --job-name=AR1_estimation
#SBATCH --output=AR1_estimation_%j.out
#SBATCH --error=AR1_estimation_%j.err
#SBATCH --ntasks=1
#SBATCH --cpus-per-task=8
#SBATCH --mem-per-cpu=2G
#SBATCH --time=02:00:00
#SBATCH --partition=bigmem  # bigmem


module load r/3.6.3


Rscript myrscript.R --ncores 1 --repl 100 --task 1




[zye2@hopper2 stat778-week7]$ sbatch run_ar1.sh
Submitted batch job 3251421
[zye2@hopper2 stat778-week7]$ sacct -j 3251421 -o JobID,JobName,Elapsed,TotalCPU,State,ExitCode
JobID           JobName    Elapsed   TotalCPU      State ExitCode 
------------ ---------- ---------- ---------- ---------- -------- 
3251421      AR1_estim+   00:53:14  53:14.742  COMPLETED      0:0 
3251421.bat+      batch   00:53:14  53:14.741  COMPLETED      0:0 
3251421.ext+     extern   00:53:14   00:00:00  COMPLETED      0:0 

### Activity 7

#!/bin/bash
#SBATCH --job-name=AR1_array
#SBATCH --output=AR1_array_%A_%a.out
#SBATCH --error=AR1_array_%A_%a.err
#SBATCH --ntasks=1
#SBATCH --cpus-per-task=4
#SBATCH --mem-per-cpu=2G
#SBATCH --time=02:00:00
#SBATCH --array=1-10
#SBATCH --partition=normal

module load r/3.6.3


Rscript myrscript.R --ncores 1 --repl 100 --task ${SLURM_ARRAY_TASK_ID}



[zye2@hopper2 stat778-week7]$ sbatch run_ar1_array.sh
Submitted batch job 3251509

[zye2@hopper2 stat778-week7]$ sacct -j 3251509 -o JobID,JobName,Partition,State,Elapsed,TotalCPU
JobID           JobName  Partition      State    Elapsed   TotalCPU 
------------ ---------- ---------- ---------- ---------- ---------- 
3251509_1     AR1_array     bigmem  COMPLETED   00:53:36  53:58.979 
3251509_1.b+      batch             COMPLETED   00:53:36  53:58.978 
3251509_1.e+     extern             COMPLETED   00:53:36   00:00:00 
3251509_2     AR1_array     bigmem  COMPLETED   00:53:31  53:44.837 
3251509_2.b+      batch             COMPLETED   00:53:31  53:44.835 
3251509_2.e+     extern             COMPLETED   00:53:31  00:00.001 
3251509_3     AR1_array     bigmem  COMPLETED   00:54:46  54:41.812 
3251509_3.b+      batch             COMPLETED   00:54:46  54:41.810 
3251509_3.e+     extern             COMPLETED   00:54:46  00:00.001 
3251509_4     AR1_array     bigmem  COMPLETED   00:53:40  53:36.816 
3251509_4.b+      batch             COMPLETED   00:53:40  53:36.815 
3251509_4.e+     extern             COMPLETED   00:53:40   00:00:00 
3251509_5     AR1_array     bigmem  COMPLETED   00:53:05  53:01.005 
3251509_5.b+      batch             COMPLETED   00:53:05  53:01.003 
3251509_5.e+     extern             COMPLETED   00:53:05  00:00.001 
3251509_6     AR1_array     bigmem  COMPLETED   00:53:00  52:54.157 
3251509_6.b+      batch             COMPLETED   00:53:00  52:54.155 
3251509_6.e+     extern             COMPLETED   00:53:00  00:00.001 
3251509_7     AR1_array     bigmem  COMPLETED   00:53:08  53:59.902 
3251509_7.b+      batch             COMPLETED   00:53:08  53:59.900 
3251509_7.e+     extern             COMPLETED   00:53:08  00:00.001 
3251509_8     AR1_array     bigmem  COMPLETED   00:53:51  54:47.563 
3251509_8.b+      batch             COMPLETED   00:53:51  54:47.562 
3251509_8.e+     extern             COMPLETED   00:53:51  00:00.001 
3251509_9     AR1_array     bigmem  COMPLETED   00:53:03  52:56.954 
3251509_9.b+      batch             COMPLETED   00:53:03  52:56.953 
3251509_9.e+     extern             COMPLETED   00:53:04  00:00.001 
3251509_10    AR1_array     bigmem  COMPLETED   00:53:07  53:03.567 
3251509_10.+      batch             COMPLETED   00:53:07  53:03.565 
3251509_10.+     extern             COMPLETED   00:53:07  00:00.001

